Preprocess

### 2024-03-18 src/preprocess.Rmd
Plotted gpt3 v2a results from andy for rd1to2
Update manuscript plots with gpt3 v2a results from andy
Final gpt3/4 results from andy - first icd as pred

            "../tmp/healsl_rd1_rapid_gpt3_v2.csv",

@@

        ) %>% mutate(round = 1),

@@

            "../tmp/healsl_rd2_rapid_gpt3_v2.csv",

@@

        ) %>% mutate(round = 2)

@@

            "../tmp/healsl_rd1_rapid_gpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")

@@

            "../tmp/healsl_rd2_rapid_gpt4_v1.csv",
            col_select = c("rowid", "round", "api_chat_icd")

@@

    ) %>% rename(gpt4_icd10 = api_chat_icd),

>>>>

            "../tmp/healsl_rd1_rapid_gpt3_v2b_first.csv",

@@

        ) %>% mutate(
            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
            round = 1

@@

            "../tmp/healsl_rd2_rapid_gpt3_v2b_first.csv",

@@

        ) %>% mutate(
            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
            round = 2

@@

            "../tmp/healsl_rd1_rapid_gpt4_v2b_first.csv",
        ) %>% mutate(
            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
            round = 1

@@

            "../tmp/healsl_rd2_rapid_gpt4_v2b_first.csv",
        ) %>% mutate(
            cause1_icd10 = str_sub(cause1_icd10, 1, 3),
            round = 2

@@

    ) %>% rename(gpt4_icd10 = cause1_icd10),
